Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization

### 2020-11-15 latex/tex/ack.tex

@@

The authors would like to thank Simin Ma for contributions to the algorithmic analysis and John Farrell for his contributions to the implementation of the parallel algorithm.

>>>>

%!TEX root = ../paper.tex

@@

%\small
This material is based upon work supported by the National Science Foundation under Grant No. OAC-1642385 and OAC-1642410.
This manuscript has been co-authored by UT-Battelle, LLC under Contract No. DE-AC05-00OR22725 with the U.S. Department of
Energy. This project was partially funded by the Laboratory Director's Research and Development fund. This research used resources
of the Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory, which is supported by the Office of Science of
the U.S. Department of Energy.

The authors would like to thank Simin Ma for contributions to the algorithmic analysis and John Farrell for his contributions to the implementation of the parallel algorithm.
%\normalsize

### 2020-11-15 latex/tex/conclusion.tex

One approach for reducing the bandwidth cost of Rank-2 NMF is to choose a more balanced data distribution over a 2D grid, as proposed by Kannan et al. \cite{KBP16}.
This will reduce the communicated data and achieve a local data matrix that is more square, which can improve local matrix multiplication performance.
The downside of this approach is that it requires a redistribution of the data for each split, but if many NMF iterations are required, then the single upfront redistribution cost may be amortized.

>>>>

One approach for reducing the bandwidth cost of Rank-2 NMF is to choose a more balanced data distribution over a 2D grid, as proposed by Kannan et al. \cite{KBP16}.
This will reduce the communicated data and achieve a local data matrix that is more square, which can improve local matrix multiplication performance.
The downside of this approach is requiring a redistribution of the data for each split, but if many NMF iterations are required, then the single upfront cost may be amortized.
